Declarative Integration of Interactive 3D Graphics into the World-Wide Web:\\Principles, Current Approaches, and Research Agenda

### 2013-04-29 Web3D2013-Dec3D/paper.tex
Minor updates

\emph{XML3D} \cite{Sons2010} is a collaboration of DFKI and Intel VCI. Similar to X3DOM, it employs CSS3, DOM scripting, and DOM events. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON.

@@

There are two implementations of XML3D: The native implementation based on a  modified Chromium browser, and xml3d.js~\cite{sons:2013}, a Polyfill implementation based on WebGL and JavaScript.

Both platforms are available under an Open Source license and used in many national and international research and industrial projects. From the user feedback and use cases we have collected from both evaluation platforms, we were able to derive the essential features, that both approaches have in common and that we propose for a Dec3D standard.

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  %\vspace{-0.2cm}
\end{figure}

@@

Besides this, we further distinguish between essential Dec3D DOM Elements, were the focus lies on a minimalistic element set, as well as more comprehensive Dec3D DOM Elements (see middle of Figure \ref{fig:polyArch}), which build on top of those with the focus on usability and which for convenience could build on existing scene-graph standards such as X3D ~\cite{Web3D-X3D} or COLLADA~\cite{Arnaud06}.

>>>>

\emph{XML3D} \cite{Sons2010} is a result of collaboration of DFKI and Intel VCI. Similarly to X3DOM, it employs CSS3, DOM scripting, and DOM events. In contrast to X3DOM, XML3D is designed as a extension to HTML5 from scratch. It does not define a scene-graph, but uses the DOM tree structure for parent child relations and second level references e.g\ via CSS to (re-)use resources such as geometry data, material descriptions or animation data. These resources are not necessarily in the same document, but can also come from external documents in various formats, e.g. as JSON.

@@

There are two implementations of XML3D: the native implementation based on a  modified Chromium browser, and xml3d.js~\cite{sons:2013}, a Polyfill implementation based on WebGL and JavaScript. Both platforms are available under an Open Source license and used in many national and international research and industrial projects. From the user feedback and use cases we have collected from both evaluation platforms, we were able to derive the essential features, that both approaches have in common and that we propose for a Dec3D standard.

\begin{figure}
  \centering
  \includegraphics[width=1.0\linewidth]{images/museum_with_tags2.pdf}
  \caption{A highly dynamic declarative 3D scene with nine animated and skinned characters. The calculation is either performed with classical sequential JavaScript or in parallel exploiting Intel's River Trail proposal for parallel data computations in JavaScript.}
  \label{fig:xflow}
  \vspace{-0.2cm}
\end{figure}

@@

Besides this, we further distinguish between essential Dec3D DOM Elements, where the focus lies on a minimalistic element set, as well as more comprehensive Dec3D DOM Elements (see middle of Figure \ref{fig:polyArch}), which build on top of those with the focus on usability and which for convenience could build on existing scene-graph standards such as X3D ~\cite{Web3D-X3D} or COLLADA~\cite{Arnaud06}.
